Estimating duration using survival analysis

### 2024-08-01 cis-perfect-testing.tex
Christl comment on lack of independence within households

>>>>

A particular violation of independence is the household design of the CIS.
Individuals in the same household both have correlated infection times and correlated testing times, as they will typically have the same test schedule.
If the test schedules are truly uninformative, as assumed here, this is unlikely to introduce bias; however, further work is required to confirm this hypothesis.
